---
title: "p8105_hw5_rl3328"
author: "Ruixi Li"
date: "2023-11-03"
output: html_document
---

```{r setup, message=FALSE}
library(tidyverse)
library(readr)
```

# Problem 1

## import, clean and describe data

* I created the variable `city_state`.

```{r}
homicide = read_csv("homicide-data.csv") |>
  janitor::clean_names() |>
  dplyr::mutate(
    city_state = paste(city,",",state),
    city_state = str_replace(city_state,"Tulsa , AL", "Tulsa , OK")) 

```


the raw data have `r nrow(homicide)` records and`r ncol(homicide)` variables. Column names are `r colnames(homicide)`.The data included the location of the killing, whether an arrest was made and, in most cases, basic demographic information about each victim.

## summerize and get the proportion

* I summarized within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

* For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
p = homicide |>
  group_by(city_state) |># there's no missing in city or state variables
  summarise(total_count = n(),
            unsolved_count = sum(disposition %in% c("Closed without arrest","Open/No arrest"))) |>
  filter(city_state == "Baltimore , MD") 

prop.test(pull(p,unsolved_count), pull(p,total_count),conf.level = .95) |>
  broom::tidy() |>
  select(estimate,conf.low, conf.high)
```

## get the proportions for all locations

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

I had a function calculating prop and its 95%CI.
```{r}
prop = function(df){
  
  pp = prop.test(pull(df,unsolved_count), pull(df,total_count),conf.level = .95) |>
    broom::tidy() |>
    select(estimate,conf.low, conf.high)
}

prop(p)#check if the function works

data_city = homicide |>
  group_by(city_state) |># there's no missing in city or state variables
  summarise(total_count = n(),
            unsolved_count = sum(disposition %in% c("Closed without arrest","Open/No arrest"))) 

result <- data_city |>
  group_by(city_state) |>
  nest() |>
  mutate(proportion_test = map(data, prop)) |>
  select(proportion_test) |>
  unnest(proportion_test)

#do I need to combine the two locations in Tulsa
```

## visualization

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
result |>
  mutate(city_state = fct_reorder(city_state,estimate)) |>
  ggplot(aes(x = city_state, y = estimate, color = city_state)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high))
```

# Problem 2

## import and clean data

```{r}
longitudinal = function(path,filename) {
  
  df = 
    read_csv(path) |>
    janitor::clean_names() |>
    mutate(id = filename)
    pivot_longer(
      -id,
      names_to = "week",
      values_to = "value",
      names_prefix = "week_") |>
    separate(id,c("arm","subject_id"),sep="_") |>
    mutate(
      arm = recode(
        arm,
        con = "control",
        exp = "experimental"),
  subject_id = gsub("\\.csv\\","",subject_id))

  df
  
}
filelst = list.files("./data")
q3_tidy = 
  map(1:20, longitudinal, path = paste("./data/", filelst, sep = ""), id = filelst) |> 
  bind_rows()

q3_tidy =
  bind_rows(
    longitudinal("./data/con_01.csv","con_01"),
    longitudinal("./data/con_02.csv","con_02"),
    longitudinal("./data/con_03.csv","con_03"),
    longitudinal("./data/con_04.csv","con_04"),
    longitudinal("./data/con_05.csv","con_05"),
    longitudinal("./data/con_06.csv","con_06"),
    longitudinal("./data/con_07.csv","con_07"),
    longitudinal("./data/con_08.csv","con_08"),
    longitudinal("./data/con_09.csv","con_09"),
    longitudinal("./data/con_10.csv","con_10"),
    longitudinal("./data/exp_01.csv","exp_01"),
    longitudinal("./data/exp_02.csv","exp_02"),
    longitudinal("./data/exp_03.csv","exp_03"),
    longitudinal("./data/exp_04.csv","exp_04"),
    longitudinal("./data/exp_05.csv","exp_05"),
    longitudinal("./data/exp_06.csv","exp_06"),
    longitudinal("./data/exp_07.csv","exp_07"),
    longitudinal("./data/exp_08.csv","exp_08"),
    longitudinal("./data/exp_09.csv","exp_09"),
    longitudinal("./data/exp_10.csv","exp_10"))
    
```

